\documentclass{article}

\usepackage{amsmath,amsfonts,amssymb}

\begin{document}

\title{Games and Boolean models - mid-term exam}
\author{Giuseppe Baudo\\
{\footnotesize LM Informatics}\\
{\footnotesize University  of Bologna}}
\maketitle

{\footnotesize \textsl{Instructions:}
\begin{itemize}
\item Edit your work using the provided tex file. Hand in your work as a LaTex-generated pdf file attached to an e-mail addressed to roxyjean at gmail.com,
by the end (i.e. 24:00) of sunday 12 November 2017. Your name should appear both as the author above, and in the chosen tex/pdf files names.

\item All solution methods and corresponding computations have to be carefully commented, either in English or in Italian. Any part of the work consisting of
non-commented computations and/or expressions shall be disregarded.
\end{itemize}
}

\section{Exercise}
For an even integer $m$, let $M=\{1,\ldots,m\}$ and define $f:M\rightarrow M$ by
$$f(k)=\left\{\begin{array}{c}\frac{m}{2}+k\text{ if }1\leq k\leq\frac{m}{2}\text ,\\ k-\frac{m}{2}\text{ if }\frac{m}{2}<k\leq m\text .\end{array}\right .$$
\begin{enumerate}
\item Characterize binary relation $R^f$ on $M$ defined by
$$R^f=\{(k,f(k)):1\leq k\leq m\}\subset M\times M$$
in terms of (ir)reflexivity, (a/anti)symmetry, transitivity and completeness. Determine the number of 1s in Boolean matrix $\mathcal M^{R^f}\in\{0,1\}^{m\times m}$
representing $R^f$, i.e.
$\mathcal M_{kl}^{R^f}=\left\{\begin{array}{c}1\text{ if }(k,l)\in R^f\text ,\\0\text{ if }(k,l)\in M\times M\backslash R^f\text ,\end{array}\right .$
$1\leq k,l\leq m$.

\item Identify a ($\supseteq$-)minimal rational preference (binary relation) $R^{\succsim^*}$ satisfying $R^{\succsim^*}\supseteq R$. How many 1s are in
Boolean matrix $\mathcal M^{R^{\succsim^*}}$? Also determine the corresponding ordered partition $\mathfrak P^{\succsim^*}=(A_1,\ldots,A_{|\mathfrak P^{\succsim^*}|})$
of $M$.
\end{enumerate}

\section{Exercise}
For player set $N=\{1,\ldots ,n\}$ and strategy set $\mathbb S_i=\{0,1\}$ for all $i\in N$, let
$$u_i(s)=u_i(s_i,s_{-i})=\left(s_i-\sum_{j\in N}\frac{s_j}{n}\right)^2\text{ for all strategy profiles }s\in\{0,1\}^n\text .$$
\begin{enumerate}
\item Is this a common interest game? If yes, then determine the (non-empty) set of strategy profiles where each player attains the maximum payoff. If no, then show
that different players have different optimal strategy profiles. Is this a constant-sum game? If yes, then show that any two strategy profiles $s,s'\in\{0,1\}^n$
provide the same aggregate payoff, that is to say $\sum_{i\in N}u_i(s)=\sum_{i\in N}u_i(s)$. If no, then show that there are different strategy profiles providing
different aggregate payoffs. Are there Pareto-dominated strategy profiles? If yes, then determine all pairs of strategy profiles one of which Pareto-dominates the
other. If no, then show that for any pair of strategy profiles neither one Pareto-dominates the other.

\item Regarding this as a congestion game with a 2-set $\{0,1\}$ of facilities, denote by $u_0(k)$ the utility attained by playing 0 when the number of those playing 0
is $k$ and by $u_1(k)$ the utility attained by playing 1 when the number of those playing 1 is $k$. Verify whether the game is monotone and, in particular, whether
$$u_0(k)-u_0(k+1)=u_1(k)-u_1(k+1)$$ for all $1\leq k<n$. For $1<k<n$, denote by $s_0^k\in\{0,1\}^n$ any of the $\binom{n}{k}$ strategy profiles where $k=|\{i:s_i=0\}|$,
and by $\textbf P:\{0,1\}^n\rightarrow\mathbb R$ the exact potential function. Determine $\textbf P(s_0^k)$. Is there any relation between the set of strong equilibria
and the set of equilibria (with non-random strategies)? How many equilibria are there?

\item Verify whether the $n$-tuple of random strategies $\frac{\textbf 1}{\textbf 2}\in[0,1]^n$ where every $i\in N$ plays both 0 and 1 with equal probability, i.e.
$\frac{1}{2}$, is an equilibrium. 
\end{enumerate}

\section{Exercise}
For $M=\{1,\ldots,m\}$, consider the symmetric congestion game where every player $i\in N=\{1,\ldots,n\}$ has strategy set $\mathbb S_i=\mathcal K\subset 2^{2^M}$
consisting of the $m!$ \textit{maximal chains} $\{A_0,A_1,\ldots,A_{m-1},A_m\}\in\mathcal K$ of subsets of $M$. That is,
$$M=A_m\supset^*A_{m-1}\supset^*\cdots\supset^*A_1\supset^*A_0=\emptyset\text{, where }$$
$$A_k\supset^*A_{k-1}\Leftrightarrow A_k\supset A_{k-1},|A_k|=|A_{k-1}|+1\text{ }(1\leq k\leq m)$$
is the \textit{covering relation}. Hence the set of facilities is $\{A:\emptyset\subset A\subset M\}$. For every strategy profile $s=(s_1,\ldots,s_n)\in\mathcal K^n$,
denote $i$'s strategy ($i\in N$) by
$$s_i=\{A_0,A_1^i,\ldots,A_{m-1}^i,A_m\}\in\mathcal K\text ,$$
and define congestion vector $\{c_A(s):\emptyset\subset A\subset M\}\in\mathbb Z_+^{2^m-2}$ by
$$c_A(s)=|\{i:A\in s_i\}|\text .$$
Finally, utilities have form
$$u_i(s)=\sum_{0<k<m}\frac{1}{c_{A^i_k}(s)}\text .$$
In what follows, distinguish between cases (a) $n\leq m$ and (b) $n=m!$.
\begin{enumerate}
\item Is this a common interest game? If yes, then determine the (non-empty) set of strategy profiles where each player attains the maximum payoff. If no, then show
that different players have different optimal strategy profiles. Is this a constant-sum game? If yes, then show that any two strategy profiles $s,s'\in\{0,1\}^n$
provide the same aggregate payoff, that is to say $\sum_{i\in N}u_i(s)=\sum_{i\in N}u_i(s)$. If no, then show that there are different strategy profiles providing
different aggregate payoffs. Are there Pareto-dominated strategy profiles? If yes, then provide examples of pairs of strategy profiles one of which Pareto-dominates the
other. If no, then show that for any pair of strategy profiles neither one Pareto-dominates the other.
\item Characterize the set of equilibria and the set of strong equilibria (with non-random strategies). Compute the value $\textbf P(s)$ taken by the exact potential
\textbf P at any equilibrium $s$.
\item Verify whether the random strategy profile consisting of $n$ uniform distributions over the $m!$-set $\mathcal K$ of maximal chains is an equilibrium or not.
\end{enumerate}

\section{Exercise}
Let $M=\{1,\ldots,10\}$ and define $f:M\rightarrow\{0,1\}$ by
$f(i)=\left\{\begin{array}{c}1\text{ if }i\text{ is a prime,}\\0\text{ otherwise.}\end{array}\right .$
Compute the discrete Choquet integral $E_{\eta}^C(f)$ of $f$ with respect to fuzzy probability $\eta:2^M\rightarrow[0,1]$ defined by
$$\eta(A)=\binom{11}{2}^{-2}\left(\sum_{i\in A}i\right)^2\text{ for all }A\in 2^M\text .$$


\end{document}
